---
title: "Today's Agenda"
editor_options: 
  chunk_output_type: console
execute:
  
  message: false
  warning: false
  echo: false
from: markdown+emoji
---

```{r}
#library(tidyverse)
library(dplyr)
library(purrr)
library(gt)
today_ymd <- Sys.Date()
today <- format(today_ymd,"%a %b %d")


agenda_final <- read.csv("documents/agenda_final.csv")%>% 
  mutate(time = today_ymd - as.Date(date_ymd) )

val <- ifelse(max(agenda_final$time)<0,
              max(agenda_final$time),
              min(agenda_final$time[agenda_final$time>=0]) )


agenda_today <- agenda_final %>% filter(time == val)

```

## [Class: Finals Week]{style="color: #4E2A84;"}

<!-- ```{r} -->

<!-- agenda_today %>%  -->

<!--   select(callout) %>%  -->

<!--   mutate(callout = ifelse(callout != "", map(paste0({fontawesome::fa('triangle-exclamation')}, callout), glue::glue), "NA")) %>%  -->

<!--   t() %>%  -->

<!--   as.data.frame() %>%  -->

<!--   filter(V1 != "NA") %>%  -->

<!--   gt() %>%  -->

<!--   fmt_markdown(columns = c(V1) )%>% -->

<!--   cols_align(align = "left") %>%  -->

<!--   tab_options(column_labels.hidden = TRUE, -->

<!--               table.align = "left", -->

<!--               table_body.border.top.color = "white", -->

<!--               table_body.border.bottom.color = "white", -->

<!--               table_body.hlines.color = "white", -->

<!--               table.width = pct(100)) -->

<!-- ``` -->

The exam retake is online via Zoom <https://northwestern.zoom.us/j/99863923813>

-   You must have your camera **on and appropriately positioned** or you will receive a 0.

-   Your submission time on Canvas must be **prior** to logging off Zoom.

- ANU students attend at same time and location (your end time will be adjusted for your accommodation)

- Strongly suggest arriving a few minutes early - if you are late due to technical issues **that is your exam time**.

You must have a Northwestern Zoom account to join <https://northwestern.zoom.us/> You cannot be logged into a personal account or an account through a different university.

## Take Exam

You can either take the exam **Tuesday 3/12 at 5:30pm central** (exam must be submitted before 6:30pm or your ANU time *or it will not be graded*) or **Friday 3/15 at 9am central** (exam must be submitted before 10am or your ANU time *or it will not be graded*)

<br>

-   [Retake Exam 1](https://posit.cloud/spaces/321338/content/7216900)
-   [Retake Exam 2](https://posit.cloud/spaces/321338/content/7199520)
-   [Retake Exam 3](https://posit.cloud/spaces/321338/content/7199532)

<br>

## Submit Exam

-   [Submit Exam 1 Retake](https://canvas.northwestern.edu/courses/204767/assignments/1328817)
-   [Submit Exam 2 Retake](https://canvas.northwestern.edu/courses/204767/assignments/1328819)
-   [Submit Exam 3 Retake](https://canvas.northwestern.edu/courses/204767/assignments/1328821)

<br><br>

```{r echo = FALSE}
knitr::knit_exit()
```
