---
title: "Today's Agenda"
editor_options: 
  chunk_output_type: console
execute:
  
  message: false
  warning: false
  echo: false
from: markdown+emoji
---


```{r}
#library(tidyverse)
library(dplyr)
library(purrr)
library(gt)
today_ymd <- Sys.Date()
today <- format(today_ymd,"%a %b %d")


agenda_final <- read.csv("documents/agenda_final.csv")%>% 
  mutate(time = today_ymd - as.Date(date_ymd) )

val <- ifelse(max(agenda_final$time)<0,
              max(agenda_final$time),
              min(agenda_final$time[agenda_final$time>=0]) )


agenda_today <- agenda_final %>% filter(time == val)

```

## [Class: Wed Dec 06]{style="color: #4E2A84;"}

<!-- ```{r} -->
<!-- agenda_today %>%  -->
<!--   select(callout) %>%  -->
<!--   mutate(callout = ifelse(callout != "", map(paste0({fontawesome::fa('triangle-exclamation')}, callout), glue::glue), "NA")) %>%  -->
<!--   t() %>%  -->
<!--   as.data.frame() %>%  -->
<!--   filter(V1 != "NA") %>%  -->
<!--   gt() %>%  -->
<!--   fmt_markdown(columns = c(V1) )%>% -->
<!--   cols_align(align = "left") %>%  -->
<!--   tab_options(column_labels.hidden = TRUE, -->
<!--               table.align = "left", -->
<!--               table_body.border.top.color = "white", -->
<!--               table_body.border.bottom.color = "white", -->
<!--               table_body.hlines.color = "white", -->
<!--               table.width = pct(100)) -->
<!-- ``` -->


The exam retake is online via Zoom. You must have your camera **on and appropriately positioned** or you will receive a 0.

[https://northwestern.zoom.us/j/99863923813](https://northwestern.zoom.us/j/99863923813)

Strongly suggest arriving a few minutes early - if you are late due to technical issues that is your exam time.

You must have a Northwestern Zoom account to join [https://northwestern.zoom.us/](https://northwestern.zoom.us/)
You cannot be logged into a personal account or an account through a different university.


## Take Exam

You must take the exam with **your section** at the designated exam start time.

### Section 21 (Kuyper) Wed 12/6 9am

- [Retake Exam 1](https://posit.cloud/spaces/321338/content/7199546)
- [Retake Exam 2](https://posit.cloud/spaces/321338/content/7199507)
- [Retake Exam 3](https://posit.cloud/spaces/321338/content/7199524)

<br>

### Section 20 (Sass) Wed 12/6 3pm

- [Retake Exam 1](https://posit.cloud/spaces/321338/content/7199541)
- [Retake Exam 2](https://posit.cloud/spaces/321338/content/7199520)
- [Retake Exam 3](https://posit.cloud/spaces/321338/content/7199532)

<br>

## Submit Exam

- [Submit Exam 1 Retake](https://canvas.northwestern.edu/courses/201484/assignments/1284081?module_item_id=2781435)
- [Submit Exam 2 Retake](https://canvas.northwestern.edu/courses/201484/assignments/1284083?module_item_id=2781436)
- [Submit Exam 3 Retake](https://canvas.northwestern.edu/courses/201484/assignments/1284085?module_item_id=2781437)

<br><br>

```{r echo = FALSE}
knitr::knit_exit()
```
